Title here

### 2016-12-21 portfolio/text/ms.Rmd
Develop discussion

For individuals deriving livelihoods from natural resources, theory suggests
that adopting strategies with a diversity of assets provides substantial
benefits over strategies with lower diversity [REFS]. However, the ability to
effectively diversify in practice is limited by regulation and market forces.
Here we document the effect of changing species diversity on revenue and revenue
variability across three scale. Each scale reflects individual-level choices
that produce varied levels of species diversity. We find that individuals
fishing permit sets that allow high levels of species diversity tend to have
lower revenue variability. Adding an additional fisheries permit usually
increases revenue and decreases revenue variability. However, within the
constraints of a permit and accounting for effort, specializing (reducing
species diversity) tends to increase revenue and specializing or generalizing
tends to be associated with greater revenue variability, with considerable
differences across fisheries. Thus, the most effective mechanism by which
species diversity can lower revenue variability for individual fishers ---
switching or adding fishing permits --- is often costly, limited by regulations,
and consequently unavailable to many individuals in practice.

Our results shows additional support for the idea that individual fishers can
reduce their income variability by diversifying their catch portfolios. However,
most individuals do not appear to change their catch diversity substantially
from year to year, and most strategies adopted by Alaskan fishermen lie in
a high-risk, high-reward quadrant in which reducing diversification increases
both revenue variability and expected revenue. Previous work has suggested that
changes to fisheries management such as limited entry or catch share programs
may inadvertently act as barrier to diversification and promote specializing
(Hilborn et al. 2003; Kasperski and Holland 2013). While some of these
specialized fishing strategies may be associated with increased revenue
variability, the benefit may be that they are also associated with increased
revenue. External market forces may interact in concert with management
regulations to promote specialization for fishers or other individuals dependent
on natural resources. In terrestrial agriculture for instance, there are also
many instances of specializing being profitable; drivers include the ability to
specialize on high-profit cash crops (tobacco, cocoa), the availability of
government agricultural subsidies (soybeans, corn in the USA), and farming on
a large industrial scale. With increasing environmental variability and extreme
events in a changing climate (REF), it is particularly important that
individuals who rely on natural resources as a primary source of income have
strategies to reduce risk. Though variability in individual revenues may not be
actively incorporated into many management decisions, analyses like ours help to
understand the range of diversification strategies available and how their
benefits may change over time.

Our work compliments previous results that have examined the effects of species diversity at the 
community (Ref) and vessel(Ref) level that show THIS (Sethi, Kasperski, others)

### Reconciling the effects at different levels of species diversity

- why variability/uncertainty might increase with changes in diversity...

- and how fit in with @kasperski2013, @sethi2012b, @sethi2014

- part of the difference is individuals vs vessels. E.g. @kasperski2013
  suggested that diversity declined following IFQs for halibut sablefish
  vessels. The reason for the decline was that the vessels were allowed to fish
  halibut for more days (because people were sharing boats). At the level of
  people, we wouldn't expect the diversity of someone who only had
  halibut/sablefish permit to be affected by IFQs. The person, not the vessel
  holds the quota share: https://alaskafisheries.noaa.gov/fisheries/ifq

- year to year risky... But maybe evens out/better over time

- diversity within permit - often bycatch, limited room for intentional
  diversification (unless you have a M or salmon permit)

- risk results not really risk, but unpredictability given our covariates ...
  don't change anything and it's most predictable how well you'll do. What's
  unpredictable in our model, might be more predictable on a year to year,
  species by species basis for individual permit holder

- CV vs year-to-year effect for one person

Other:

- specializing can be profitable within some fisheries. Eric: analog here in
  farming literature is that diversification for small scale farmers generally
  good, except when they specialize on high demand/high value crops (tobacco,
  cocoa). Seems like benefits of diversification are also smaller for
  large-scale industrial farmers.

### Limitations + obvious extensions

There are a number of limitations to our model and extensions that could further
our understanding of the role of diversification...

- could vary by time and vary by mean diversity

- spatial/geographic variation

- nonlinear effects

- response to specific events like EVOS

@@

### Conclusions + recommendations

- bring it out to wider than fisheries (farming, timber industry, ...)

- 2 dimensions to think about (revenue and variability); and the trade-off is
  fishery specific: effects within a permit strategy are permit specific;
  sometimes make more money by specializing... some highly variable single
  species permits make a ton of money

- broadly, diversification can provide a powerful form of protection from
  multiple sources of risk to income for those that rely on extracting natural
  resources, but not all forms of diversification are equal, and on an
  individual level there can be economic benefits to specializing and risks to
  adjusting ones strategy

- with increasing environmental variability and extremes due to climate change
  those that rely on natural resources for their livelihoods need approaches to
  buffer risk more than ever

- regulations that limit the ability to diversify can have other considerable
  benefits but it's important to be aware of trade-offs inherent in these
  regulations when making management decisions

We fit a hierarchical variance-function regression model to 30 years of
commercial fisheries revenue data in Alaska to simultaneously estimate the
effect of changes in species diversity on individual's revenue and revenue
variability.

>>>>

For individuals deriving livelihoods from natural resources, theory suggests
that adopting strategies with a diversity of assets provides substantial
benefits over strategies with lower diversity [REFS]. However, the ability of
individuals to effectively diversify is limited by regulation and market forces
in practice. Here we document the effect of changing species diversity on
revenue and revenue variability across three scale. Each scale reflects
individual-level choices that can affect species diversity. We find that
individuals with fishing permit sets that allow high levels of species diversity
tend to have lower revenue variability. Adding a fisheries permit usually
increases revenue and decreases revenue variability. Within the constraints of
a permit and accounting for effort, specializing (reducing species diversity)
tends to increase revenue while both specializing or generalizing tends to be
associated with greater revenue variability - though there are considerable
differences among fisheries. Thus, the most effective mechanism by which species
diversity can lower revenue variability for individual fishers --- switching or
adding fishing permits --- is costly, limited by regulations, and consequently
unavailable to many individuals in practice.

TODO: cut apart and recombine the following couple chunks:

Our results provide additional support for the idea that individual fishers can
reduce their income variability by diversifying their catch portfolios. However,
most individuals do not appear to change their catch diversity substantially
from year to year [OLE: is there a supplemental figure or statistic that speaks
to this point?], and most strategies adopted by Alaskan fishermen lie in
a high-risk, high-reward quadrant in which reducing diversification increases
both revenue variability and expected revenue. Previous work has suggested that
changes to fisheries management such as limited entry or catch share programs
may inadvertently act as barrier to diversification and promote specializing
(Hilborn et al. 2003; Kasperski and Holland 2013). While some of these
specialized fishing strategies may be associated with increased revenue
variability, the benefit may be that they are also associated with increased
revenue.

Worldwide, fisheries confront the challenge of sustainable management (). While
many fisheries are well managed and productive, many are also rebuilding from
periods of over-exploitation (Worm et al. Science 2009). A common tactic to aid
in fisheries rebuilding is to modify regulations to reduce the unintended
harvest rebuilding stocks while allowing the continued harvest of healthy stocks
(need REF). Such bycatch reduction is an important goal for both ecological
(Crowder and Murawski 1998, Lewison et al. 2004) and economic (Curtis and Hicks
2000; Chakravorty and Nemoto 2001) reasons. Cumulatively, though, regulatory
changes for bycatch reduction as well as other reasons gradually lead to
fisheries that target one or a few species and individual fishers wishing to
participate in multiple fisheries must own (or purchase) multiple permits. Thus
a general consequence of fisheries regulations that are shown to improve
sustainability of fish stocks and avoid overfishing - including improved
assessments (Hilborn and Ovando 2014) and individual quota systems (Costello et
al. 2008 ) - may ultimately restrict individual diversification or at least make
developing a diverse fishing portfolio more costly. Add Alaska example of
IFQs...?

<!-- Chakravorty, U. and Nemoto, K. (2001) Modeling the effects of area closure
and tax policies: a spatial-temporal model of the hawaii longline fishery.
Marine Resource Economics 15, 179–204.

Costello C, Gaines SD, Lynham J (2008) Can catch shares prevent fisheries
collapse? Science 321(5896):1678–1681

Crowder, L.B. and Murawski, S.A. (1998) Fisheries bycatch: implications for
management. Fisheries Management 23, 8–17.

Curtis, R. and Hicks, R.L. (2000) The Cost of sea turtle preservation: the case
of Hawaii’s Pelagic longliners. American Journal of Agricultural Economics 82,
1191– 1197.

Hilborn R, Ovando D. 2014 Reflections on the success of traditional fisheries
management. ICES J. Mar. Sci. 71, 1040–1046.

Lewison, R.L., Crowder, L.B., Rimprove fishing gear ead, A.J. and Freeman, S.A.
(2004) Understanding impacts of fisheries bycatch on marine megafauna. Trends in
Ecology & Evolution 19, 598–604.

Read, A.J., Drinker, P. and Northridge, S. (2006) Bycatch of marine mammals in
US and global fisheries. Conservation Biology 20, 163–169. -->

<!-- Reconciling the different levels of effects -->

Our findings across fishing strategies are in line with previous findings
[@kasperski2013, @sethi2012b, @sethi2014], but we also found that, for
individuals, specializing tended to be associated with increased revenue and
altering species diversity tended to be associated with increased revenue
variability. Specializing has been shown to be profitable in some circumstances
for other natural resource sectors. For example, while diversification is
generally helpful for small-scale farmers, farmers that specialize on
high-demand and high-value crops such as tobacco or cocoa can benefit, at least
in the short term, from specializing on these crops (REF). In terms of variance,
there are number of reasons by annual revenue variability might be expected to
increase with changes to individual fished species diversity. First, changes to
fishing patterns will sometimes be associated with a learning or adaptation
phase as individuals become accustomed to new locations, new gear, or new
species. Secondly, changes in diversity might reflect years in which targeted
species were less available and fishers were forced to target other species or
landed more bycatch. Most importantly, this increased variability technically
reflects an inability for our large-scale model to predict an individual's
revenue in a subsequent year. There are many reasons, often unique to an
individual permit holder and therefore not included in a large-scale model, that
might make that specific individual's revenue less predictable given a change in
species diversity compared to not changing species diversity from one year to
the next.

<!--In terrestrial agriculture for instance, there are many instances of
specializing being profitable; drivers include the ability to specialize on
high-profit cash crops (tobacco, cocoa), the availability of government
agricultural subsidies (soybeans, corn in the USA), and farming on a large
industrial scale (REF).-->

<!-- Limitations + obvious extensions paragraph -->

Our analysis provides a synthetic view of the effects of species diversity on
individuals over 30 years in one of the most productive fishing regions in the
world. However, our analysis simultaneously uses data from across the broad
geography of Alaska and over 30 years, potentially obscuring regional or
time-variation in the consequences of diversification on revenue and revenue
variability. We expect future research examining diversification over finer
spatial and temporal scales will uncover additional interesting relationships.
Furthermore, in addressing the overall pattern, we have averaged out several
major discrete events (e.g., the Exxon Valdez oil spill in 1989) that had
significant consequences for the ecosystem and social system in Alaska (general
EVOS consequences REF). We do not wish to minimize the important of such events,
but note that it is important to understand the benefits of diversification in
the context of rare and extreme disturbances which occur in marine systems
worldwide.

@@

<!-- Conclusions + recommendations

- bring it out to wider than fisheries (farming, timber industry, ...)
- 2 dimensions to think about (revenue and variability); and the trade-off is
  fishery specific: effects within a permit strategy are permit specific;
  sometimes make more money by specializing... some highly variable single
  species permits make a ton of money
- broadly, diversification can provide a powerful form of protection from
  multiple sources of risk to income for those that rely on extracting natural
  resources, but not all forms of diversification are equal, and on an
  individual level there can be economic benefits to specializing and risks to
  adjusting ones strategy 
- with increasing environmental variability and extremes due to climate change
  those that rely on natural resources for their livelihoods need approaches to
  buffer risk more than ever 
- regulations that limit the ability to diversify can have other considerable
  benefits but it's important to be aware of trade-offs inherent in these
  regulations when making management decisions 
-->

External market forces may interact in concert with management regulations to
promote specialization for fishers or other individuals dependent on natural
resources. With increasing environmental variability and extreme events in
a changing climate (REF), it is particularly important that individuals who rely
on natural resources as a primary source of income have strategies to reduce
risk. Though variability in individual revenues may not be actively incorporated
into many management decisions, analyses like ours help to understand the range
of diversification strategies available and how their benefits may change over
time.
